
load libraries
```{r}
library(arules)
library(arulesViz)
library(knitr)
library(plyr)
library(dplyr)
library(RColorBrewer)
library(stringr)
library(writexl)
library(feather)
library(xtable)
```

Load datasets
```{r}
MLFeat <- 
  read_excel(path ="C:/.../Features.xlsx", na = c ("NA", "#N/A N/A", "#N/A Field Not Applicable", "#N/A Invalid Security"))


California_20_23 <- read_feather("C:.../California_20_23.feather")


```

Add median (and mean) of S1 by year and bond
```{r}
#Adding median of S1 to by year and bonds
ARL <- California_20_23 %>% group_by(ID_CUSIP, year) %>% dplyr::summarise(Med_S2 = median(S2)
                                                                    , Mea_S2 = mean(S2))

```

Label Spread based on their magnitude
```{r}


first_percentile <- quantile(ARL$Med_S2, 0.25)  
last_percentile <- quantile(ARL$Med_S2, 0.75)    

ARL <- ARL %>%
  mutate(
    Med_S2_int_labels = case_when(
      is.na(Med_S2) ~ NA_character_,
      Med_S2 == 0 ~ "S0",
      Med_S2 < 0 & Med_S2 < first_percentile ~ "S-(Extreme)",
      Med_S2 < 0 & Med_S2 >= first_percentile ~ "S-(Low)",
      Med_S2 > 0 & Med_S2 > last_percentile ~ "S+(Extreme)",
      Med_S2 > 0 & Med_S2 <= last_percentile ~ "S+(Low)",
      TRUE ~ "S0"
    )
  )



```




Adding features
```{r}
ARL <- merge(ARL, MLFeat, by = "ID_CUSIP")

```


labeling numerical features
```{r}


#replace labels  for Callability

for (i in 1:nrow(ARL)) {
  if (ARL$CALLABLE[i] == "FALSE") {
    ARL$CALLABLE[i] <- "Non-callable"
  } else {
    ARL$CALLABLE[i] <- "Callable"
  }
}




#SELF_REPRTD_GREEN_INSTR_INDCTR

ARL$SELF_REPRTD_GREEN_INSTR_INDCTR[ARL$SELF_REPRTD_GREEN_INSTR_INDCTR == "TRUE"]<-
  "YES"

#Coupon rate
cpn_intervals <- cut(ARL$CPN, breaks = c(0, 2.99, 4.999, 15), labels = c("0_3(%)", "3_5(%)", "5_8.5(%)"))

ARL <- ARL %>% mutate(CPN_Group = cpn_intervals)

#SPREAD_AT_ISSUANCE_TO_WORST
Sp_at_iss_intervals <- cut(ARL$SPREAD_AT_ISSUANCE_TO_WORST,
                           breaks = c(quantile(ARL$SPREAD_AT_ISSUANCE_TO_WORST, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c("Less than 17", "17_57", "57_100", "Higher than 100"), include.lowest = TRUE)

ARL <- ARL %>% mutate(S_AT_Iss = Sp_at_iss_intervals)


#DUR_ADJ_MID
DUR_ADJ_MID_intervals <- cut(ARL$DUR_ADJ_MID,
                           breaks = c(quantile(ARL$DUR_ADJ_MID, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c(" Less than 2.8", "2.8_4.8", "4.8_7", "Higher than 7"), include.lowest = TRUE)

ARL <- ARL %>% mutate(DAM = DUR_ADJ_MID_intervals)



#DUR_MID
DUR_MID_intervals <- cut(ARL$DUR_MID,
                           breaks = c(quantile(ARL$DUR_MID, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c("Less than 2.9", "2.9_4.9", "4.9_7.3", " Higher than 7.3"), include.lowest = TRUE)

ARL <- ARL %>% mutate(DM = DUR_MID_intervals)



#	YIELD_ON_ISSUE_DATE
Y_on_Iss_Date_intervals <- cut(ARL$YIELD_ON_ISSUE_DATE,
                           breaks = c(quantile(ARL$YIELD_ON_ISSUE_DATE, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c(" Less than 1.7", "1.7_2.4", "2.4_3.2", "Higher than 3.2"), include.lowest = TRUE)

ARL <- ARL %>% mutate(Y_OID = Y_on_Iss_Date_intervals)




#	ISSUE_PX

#1-labeling price at issuance

ARL <- ARL %>%
  mutate(
    Iss_pri._spread = case_when(
      is.na(ISSUE_PX) ~ NA_character_,
      ISSUE_PX == 100 ~ "At Par",
      ISSUE_PX < 100 ~ "At Discount",
      ISSUE_PX > 100 ~ "At Premium"
    )
  )



#AMT_ISSUED
ARL$log_AMT_ISSUED <- log(ARL$AMT_ISSUED)

Amt_issued_intervals <- cut(ARL$log_AMT_ISSUED,
                           breaks = c(quantile(ARL$log_AMT_ISSUED, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c("Less than 14", "14_15", "15_16", "Higher than 16"), include.lowest = TRUE)

ARL <- ARL %>% mutate(Amt_iss_int = Amt_issued_intervals)

#MUNI_ISSUE_SIZE
ARL$log_MUNI_ISSUE_SIZE <- log(ARL$MUNI_ISSUE_SIZE)

MUNI_ISSUE_SIZE_intervals <- cut(ARL$log_MUNI_ISSUE_SIZE,
                           breaks = c(quantile(ARL$log_MUNI_ISSUE_SIZE, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c("Less than 17", "17_18.7", "18.7_19.5", "Higher than 19.5"), include.lowest = TRUE)

ARL <- ARL %>% mutate(MUNI_ISSUE_SIZE_int = MUNI_ISSUE_SIZE_intervals)


#SHORT_AND_LONG_TERM_DEBT
ARL$Log_DEBT <- log(ARL$SHORT_AND_LONG_TERM_DEBT)

Debt_intervals <- cut(ARL$Log_DEBT,
                           breaks = c(quantile(ARL$Log_DEBT, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c("Less than 5", "5-6.5", "6.5_8", "Higher than 8"), include.lowest = TRUE)

ARL <- ARL %>% mutate(S_L_DEBT = Debt_intervals)


#8.	SALES_REV_TURN
ARL$Log_Sale_Turn <- log(ARL$SALES_REV_TURN)

Sale_intervals <- cut(ARL$Log_Sale_Turn,
                           breaks = c(quantile(ARL$Log_Sale_Turn, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c("Less than 3.5", "3.5-4.6", "4.6_6.5", "Higher than 8.5"), include.lowest = TRUE)

ARL <- ARL %>% mutate(SALES_REV_TURN_int = Sale_intervals)



#MTY-YEARS

MTY_YEARS_intervals <- cut(ARL$`MTY-YEARS`,
                           breaks = c(quantile(ARL$`MTY-YEARS`, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c(" Less than 8", "8_12.3", "12.3_17", "Higher than 17"), include.lowest = TRUE)

ARL <- ARL %>% mutate(MTY_YEARS_int = MTY_YEARS_intervals)

#ISSUE_DT and Maturity
ARL$Y_l_day <- as.Date(paste(ARL$year, "-12-31", sep = ""), format = "%Y-%m-%d")


for (i in 1:nrow(ARL)){
  ARL$Active_years[i] <- yearFraction(ymd(ARL$ISSUE_DT[i]) 
                                   , ymd(ARL$Y_l_day[i]), dayCounters = 12)
  ARL$years_to_maturity[i] <- yearFraction(ymd(ARL$Y_l_day[i]) 
                                   , ymd(ARL$MATURITY[i]), dayCounters = 12)
  
}

active_years_interval <- cut(ARL$Active_years,
                           breaks = c(quantile(ARL$Active_years, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c(" Less than 1.1", "1.1_2.3", "2.3_4.1", "Higher than 4.1"), include.lowest = TRUE)

ARL <- ARL %>% mutate(Active_years_int = active_years_interval)


years_to_maturity_interval <- cut(ARL$years_to_maturity,
                           breaks = c(quantile(ARL$years_to_maturity, na.rm = TRUE)), na.rm = TRUE,
                           labels =  c(" Less than 4.7", "4.7_9.4", "9.4_14.4", "Higher than 14.4"), include.lowest = TRUE)

ARL <- ARL %>% mutate(years_to_maturity_int = years_to_maturity_interval)





```

label missing with char "NA"
```{r}


ARL$BB_COMPOSITE[is.na(ARL$BB_COMPOSITE)] <- "Not_Rated"
ARL$SELF_REPRTD_GREEN_INSTR_INDCTR[is.na(ARL$SELF_REPRTD_GREEN_INSTR_INDCTR)] <- "Not labelled"
ARL$RTG_FITCH[is.na(ARL$RTG_FITCH)] <- "Not_Rated"
ARL$RTG_FITCH_LONG[is.na(ARL$RTG_FITCH_LONG)] <- "Not_Rated"

ARL$S_AT_Iss <- as.character(ARL$S_AT_Iss)
ARL$S_AT_Iss[is.na(ARL$S_AT_Iss)] <- "NA"

ARL$S_AT_Iss <- as.character(ARL$S_AT_Iss)
ARL$S_AT_Iss[is.na(ARL$S_AT_Iss)] <- "NA"

ARL$DAM <- as.character(ARL$DAM)
ARL$DAM[is.na(ARL$DAM)] <- "NA"


ARL$DM <- as.character(ARL$DM)
ARL$DM[is.na(ARL$DM)] <- "NA"



ARL$Y_OID <- as.character(ARL$Y_OID)
ARL$Y_OID[is.na(ARL$Y_OID)] <- "NA"



ARL$Iss_pri._spread <- as.character(ARL$Iss_pri._spread)
ARL$Iss_pri._spread[is.na(ARL$Iss_pri._spread)] <- "NA"




# ARL$Iss._pri_int <- as.character(ARL$Iss._pri_int)
# ARL$Iss._pri_int[is.na(ARL$Iss._pri_int)] <- "NA"




ARL$Amt_iss_int <- as.character(ARL$Amt_iss_int)
ARL$Amt_iss_int[is.na(ARL$Amt_iss_int)] <- "NA"





ARL$MUNI_ISSUE_SIZE_int <- as.character(ARL$MUNI_ISSUE_SIZE_int)
ARL$MUNI_ISSUE_SIZE_int[is.na(ARL$MUNI_ISSUE_SIZE_int)] <- "NA"


ARL$MTY_YEARS_int <- as.character(ARL$MTY_YEARS_int)
ARL$MTY_YEARS_int[is.na(ARL$MTY_YEARS_int)] <- "NA"




ARL$Active_years_int <- as.character(ARL$Active_years_int)
ARL$Active_years_int[is.na(ARL$Active_years_int)] <- "NA"

ARL$years_to_maturity_int <- as.character(ARL$years_to_maturity_int)
ARL$years_to_maturity_int[is.na(ARL$years_to_maturity_int)] <- "NA"


ARL$S_L_DEBT <- as.character(ARL$S_L_DEBT)
ARL$S_L_DEBT[is.na(ARL$S_L_DEBT)] <- "NA"

ARL$SALES_REV_TURN_int <- as.character(ARL$SALES_REV_TURN_int)
ARL$SALES_REV_TURN_int[is.na(ARL$SALES_REV_TURN_int)] <- "NA"


```


Add prefix for features
```{r}
ARL$BB_COMPOSITE <- paste("BB_rating", ARL$BB_COMPOSITE, sep = " : ")

ARL$MUNI_TAX_PROV <- paste("Tax", ARL$MUNI_TAX_PROV, sep = " : ")

ARL$CPN_TYP <- paste("CPN TYP", ARL$CPN_TYP, sep = " : ")

ARL$CPN_Group <- paste("CPN", ARL$CPN_Group, sep = " : ")

ARL$MARKET_ISSUE <- paste("Market", ARL$MARKET_ISSUE, sep = " : ")

ARL$CALLABLE <- paste("Call", ARL$CALLABLE, sep = " : ")

ARL$MUNI_PURPOSE <- paste("UOP", ARL$MUNI_PURPOSE, sep = " : ")

ARL$FINANCING_TYPE <- paste("FIN. TYP", ARL$FINANCING_TYPE, sep = " : ")

ARL$ISSUER_BULK <- paste("Issuer Name", ARL$ISSUER_BULK, sep = " : ")

ARL$MUNI_LONG_INDUSTRY_TYP <- paste("Issuer Sector", 
                                         ARL$MUNI_LONG_INDUSTRY_TYP, sep = " : ")
ARL$RTG_FITCH_LONG <- paste("RTG Long Rating", 
                                         ARL$RTG_FITCH_LONG, sep = " : ")
ARL$RTG_FITCH <- paste("RTG Rating", 
                                         ARL$RTG_FITCH, sep = " : ")
ARL$S_AT_Iss <- paste("S OID", 
                                         ARL$S_AT_Iss, sep = " : ")
ARL$DAM <- paste("DU_Adj_MID", 
                                         ARL$DAM, sep = " : ")
ARL$DM <- paste("DU_MID", 
                                         ARL$DM, sep = " : ")
ARL$Y_OID <- paste("Y_OID", 
                                         ARL$Y_OID, sep = " : ")

ARL$Iss_pri._spread <- paste("Pricing TYP", 
                                         ARL$Iss_pri._spread, sep = " : ")

# ARL$Iss._pri_int <- paste("Issue Price Interval", ARL$Iss._pri_int, sep = " : ")

ARL$Amt_iss_int <- paste("Issued Amt", 
                                         ARL$Amt_iss_int, sep = " : ")

ARL$MUNI_ISSUE_SIZE_int <- paste("Muni Issued Size", 
                                         ARL$MUNI_ISSUE_SIZE_int, sep = " : ")

ARL$MTY_YEARS_int <- paste("Maturity OID", 
                                         ARL$MTY_YEARS_int, sep = " : ")
ARL$SELF_REPRTD_GREEN_INSTR_INDCTR <- 
  paste("Self Rep. Gr.",  ARL$SELF_REPRTD_GREEN_INSTR_INDCTR, sep = " : ")

ARL$S_L_DEBT <- paste("Debt",  ARL$S_L_DEBT, sep = " : ")

ARL$SALES_REV_TURN_int <- paste("SALES REV",  ARL$SALES_REV_TURN_int, sep = " : ")

ARL$Active_years_int <- paste("Active years",  ARL$Active_years_int, sep = " : ")

ARL$years_to_maturity_int <- paste("R Ys to Maturity",  ARL$years_to_maturity_int, sep = " : ")


```

Removing redundant features
```{r}



ARL_final_feat_ext_S2 <- 
  ARL %>% select(!(c(Med_S2 ,CPN_TYP, CRNCY, MAKE_WHOLE_CALL_TYPE,MUNI_FORM, SUPER_SINKER,
                                  ID_CUSIP, Mea_S2, CPN, CPN_TYP,CPN_FREQ,
                                 CRNCY, ISSUE_DT, MATURITY,
                             SPREAD_AT_ISSUANCE_TO_WORST, DUR_ADJ_MID, 
                     DUR_MID,ISSUE_PX, YIELD_ON_ISSUE_DATE, AMT_ISSUED,
                     MUNI_ISSUE_SIZE, IS_SUBORDINATED, 
                     SALES_REV_TURN, log_AMT_ISSUED, log_MUNI_ISSUE_SIZE,
                     SHORT_AND_LONG_TERM_DEBT, `MTY-YEARS`, `State Code`, Region, Y_l_day,
                     Active_years, years_to_maturity, Log_DEBT, Log_Sale_Turn, S_L_DEBT,
                     SALES_REV_TURN_int, RTG_FITCH_LONG, RTG_FITCH,DM)))

```



subset dataset for each year
```{r}

ARL_2020_ext_S2 <- ARL_final_feat_ext_S2 %>%  filter(year == 2020) %>% select(!c(year))
ARL_2021_ext_S2 <- ARL_final_feat_ext_S2 %>%  filter(year == 2021) %>% select(!c(year))
ARL_2022_ext_S2 <- ARL_final_feat_ext_S2 %>%  filter(year == 2022) %>% select(!c(year))
ARL_2023_ext_S2 <- ARL_final_feat_ext_S2 %>%  filter(year == 2023) %>% select(!c(year))
ARL_t_ext_S2 <- ARL_final_feat_ext_S2 %>% select(!c(year))

```


Remove missing values
```{r}

ARL_2020_ext_S2 <- ARL_2020_ext_S2[complete.cases(ARL_2020_ext_S2),]
ARL_2021_ext_S2 <- ARL_2021_ext_S2[complete.cases(ARL_2021_ext_S2),]
ARL_2022_ext_S2 <- ARL_2022_ext_S2[complete.cases(ARL_2022_ext_S2),]
ARL_2023_ext_S2 <- ARL_2023_ext_S2[complete.cases(ARL_2023_ext_S2),]
ARL_t_ext_S2 <- ARL_t_ext_S2[complete.cases(ARL_t_ext_S2),]
```


Convert all features to factors
```{r}
ARL_2020_ext_S2 <-ARL_2020_ext_S2 %>%  mutate_all(as.factor)
ARL_2021_ext_S2 <-ARL_2021_ext_S2 %>%  mutate_all(as.factor)
ARL_2022_ext_S2 <-ARL_2022_ext_S2 %>%  mutate_all(as.factor)
ARL_2023_ext_S2 <-ARL_2023_ext_S2 %>%  mutate_all(as.factor)
ARL_t_ext_S2 <- ARL_t_ext_S2 %>% mutate_all(as.factor)
```


convert dataframe to transaction format
```{r}
#2020
Cal2022tr_ext_S2 <- ARL_2020_ext_S2 %>%
  unite(item, everything(), sep = ",")

write.csv(Cal2022tr_ext_S2, "C:/.../Cal2020tr_ext_S2.csv", quote = FALSE, row.names = FALSE)

#2021
Cal2021tr_ext_S2 <- ARL_2021_ext_S2 %>%
  unite(item, everything(), sep = ",")

write.csv(Cal2021tr_ext_S2, "C:.../Cal2021tr_ext_S2.csv", quote = FALSE, row.names = FALSE)



#2022
Cal2022tr_ext_S2 <- ARL_2022_ext_S2 %>%
  unite(item, everything(), sep = ",")

write.csv(Cal2022tr_ext_S2, "C:.../Cal2022tr_ext_S2.csv", quote = FALSE, row.names = FALSE)

#2023
Cal2023tr_ext_S2 <- ARL_2023_ext_S2 %>%
  unite(item, everything(), sep = ",")

write.csv(Cal2023tr_ext_S2, "C:/.../Cal2023tr_ext_S2.csv", quote = FALSE, row.names = FALSE)



Cal_t_tr_ext_S2 <- ARL_t_ext_S2 %>%
  unite(item, everything(), sep = ",")

write.csv(Cal_t_tr_ext_S2, "C:/.../Cal_t_tr_ext_S2.csv", quote = FALSE, row.names = FALSE)




```


Importing transaction file
```{r}

tr2020__ext_S2 <- read.transactions("C:/.../Cal2020tr_ext_S2.csv", format = "basket", sep = ",")


tr2021_ext_S2 <- read.transactions("C:/.../Cal2021tr_ext_S2.csv", format = "basket", sep = ",")

tr2022_ext_S2 <- read.transactions("C:/.../Cal2022tr_ext_S2.csv", format = "basket", sep = ",")


tr2023_ext_S2 <- read.transactions("C:/.../Cal2023tr_ext_S2.csv", format = "basket", sep = ",")

tr_ext_S2 <- read.transactions("C:/.../Cal_t_tr_ext_S2.csv", format = "basket", sep = ",")

```


Filter rules with support and confidence thresholds 
(based on the quantile of generated rules)
```{r}

PP.association.rules_ext_S2 <- apriori(tr_ext_S2, parameter = list(supp=0.01, conf=0.6, maxlen=10),appearance = list(default="lhs",rhs="S+(Extreme)"))

NP.association.rules_ext_S2 <- apriori(tr_ext_S2, parameter = list(supp=0.01, conf=0.35, maxlen=10),appearance = list(default="lhs",rhs="S-(Extreme)"))

# PNP.association.rules_ext_S2 <- apriori(tr_ext_S2, parameter = list(supp=0.01, conf=0.8, maxlen=10),appearance = list(default="lhs",rhs= c ("S+(Extreme)","S-(Extreme)")))



```

Filter rules one Itemset and  confidence 
(supp and conf are added as filtering criteria in case we had different thresholds)
```{r}

#Positive itemsets
Pquality_scores_ext_S2 <- quality(PP.association.rules_ext_S2)

Psupp_conf_ext_S2 <- Pquality_scores_ext_S2$support * Pquality_scores_ext_S2$confidence

slot(PP.association.rules_ext_S2, "quality")$supp_conf <- Psupp_conf_ext_S2
 
#Negative itemsets
Nquality_scores_ext_S2 <- quality(NP.association.rules_ext_S2)

Nsupp_conf_ext_S2 <- Nquality_scores_ext_S2$support * Nquality_scores_ext_S2$confidence

slot(NP.association.rules_ext_S2, "quality")$supp_conf <- Nsupp_conf_ext_S2



#P N itemsets
# PNquality_scores_ext_S2 <- quality(PNP.association.rules_ext_S2)
# 
# PNsupp_conf_ext_S2 <- PNquality_scores_ext_S2$support * PNquality_scores_ext_S2$confidence
# 
# slot(PNP.association.rules_ext_S2, "quality")$supp_conf <- PNsupp_conf_ext_S2



```


Second order rules
```{r}
# Filter rules with confidence greater than 0.4 or 40%
PsubRules_ext_S2_O2 <- PP.association.rules_ext_S2[quality(PP.association.rules_ext_S2)$confidence > 0.60 & quality(PP.association.rules_ext_S2)$support > 0.01 & size(PP.association.rules_ext_S2) == 2]

NsubRules_ext_S2_O2 <- NP.association.rules_ext_S2[quality(NP.association.rules_ext_S2)$confidence > 0.35 & quality(NP.association.rules_ext_S2)$support > 0.01 & size(NP.association.rules_ext_S2) == 2 ]

# PNsubRules_ext_S2_O2 <- PNP.association.rules_ext_S2[quality(PNP.association.rules_ext_S2)$confidence > 0.8 & quality(PNP.association.rules_ext_S2)$support > 0.01  ]

Ptop10subRules_ext_S2_O2 <- head(PsubRules_ext_S2_O2, n = 10, by = "confidence")

Ntop10subRules_ext_S2_O2 <- head(NsubRules_ext_S2_O2, n = 10, by = "confidence")

```



```{r}

inspect(head(Ptop10subRules_ext_S2_O2, n = 10, by = "supp_conf"))

inspect(head(Ntop10subRules_ext_S2_O2, n = 10, by = "supp_conf"))

plot(Ptop10subRules_ext_S2_O2, method = "paracoord", measure = "confidence", shading = "lift")

plot(Ntop10subRules_ext_S2_O2, method = "paracoord", measure = "confidence", shading = "lift")

```


Rules with no order limitation
```{r}

# Filter rules with confidence greater than 0.4 or 40%
PsubRules_ext_S2 <- PP.association.rules_ext_S2[quality(PP.association.rules_ext_S2)$confidence > 0.65 & quality(PP.association.rules_ext_S2)$support > 0.01 ]

NsubRules_ext_S2 <- NP.association.rules_ext_S2[quality(NP.association.rules_ext_S2)$confidence > 0.4 & quality(NP.association.rules_ext_S2)$support > 0.01  ]

# PNsubRules_ext_S2 <- PNP.association.rules_ext_S2[quality(PNP.association.rules_ext_S2)$confidence > 0.8 & quality(PNP.association.rules_ext_S2)$support > 0.01  ]

Ptop10subRules_ext_S2 <- head(PsubRules_ext_S2, n = 10, by = "confidence")

Ntop10subRules_ext_S2 <- head(NsubRules_ext_S2, n = 10, by = "confidence")


```


```{r}


inspect(head(Ptop10subRules_ext_S2, n = 10, by = "confidence"))

inspect(head(Ntop10subRules_ext_S2, n = 10, by = "confidence"))

plot(Ptop10subRules_ext_S2, method = "paracoord", measure = "support", shading = "confidence")

plot(Ntop10subRules_ext_S2, method = "paracoord", measure = "support", shading = "confidence")


```






