

%%%%%%%%%%%%%%
Load libraries
%%%%%%%%%%%%%%
```{r}
library(splines2)
library(splines)
library(mgcv)
library (RQuantLib)
library(tidyr)
library(xts)
library(plotly)
library(lubridate)
library (readxl)
library(ggplot2)
library(dplyr)
library(scatterplot3d)
library(tidyverse)
library(plot3D)
library(rgl)
library (zoo)
library(writexl)
library(YieldCurve)
library(patchwork)
library(gridExtra)
library(stargazer)
library(scales)
library(pdfetch)
library(feather)
```


%%%%%%%%%%%%%%%%%
Grouping Criteria
Callable and Non_callable Bond dataset
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}
Cal_callable <- California %>% filter(CALLABLE == "TRUE", CPN != 15)

Cal_non_callable <- California %>% filter(CALLABLE == "FALSE")

summary(Cal_non_callable$CPN)

```

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Coupon intervals:
Construct partitions based on the coupon intervals for
California (Callable and non-callable)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}
interval_non_call <- cut(Cal_non_callable$CPN, breaks = c(0, 2.99, 4.999, 7.69), labels = c("CPN_0_3", "CPN_3_5", "CPN_5_8"))
Cal_non_callable <- Cal_non_callable %>% mutate(CPN_Group = interval_non_call)

interval_call <- cut(Cal_callable$CPN, breaks = c(0, 3.5, 4.999, 8.5), labels = c("CPN_0_3.5", "CPN_3.5_5", "CPN_5_8.5"))

Cal_callable <- Cal_callable %>% mutate(CPN_Group = interval_call)
```
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Partitioning California dataset based on tax provinces
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}

#NoN-CALLABLE

#Non-callable bonds with coupon intervals of 0-3 percent
G1_nc_all <- 
  Cal_non_callable %>% 
  filter(CPN_Group == "CPN_0_3", Date >= "2020-01-01")

#Non-callable bonds with coupon intervals of 3-5 percent excluding "FED TAXABLE/ST TAX-EXEMPT" Tax province
G2_nc_op <- 
  Cal_non_callable %>%
  filter(CPN_Group == "CPN_3_5", Date >= "2020-01-01", 
         MUNI_TAX_PROV != "FED TAXABLE/ST TAX-EXEMPT")

#Non-callable bonds with coupon intervals of 3-5 percent within "FED TAXABLE/ST TAX-EXEMPT" province
G2_nc_ft <- 
  Cal_non_callable %>%
  filter(CPN_Group == "CPN_3_5", Date >= "2020-01-01", 
         MUNI_TAX_PROV == "FED TAXABLE/ST TAX-EXEMPT")

#Non-callable bonds with coupon intervals of 5-8 percent
G3_nc_all <- 
  Cal_non_callable %>% 
  filter(CPN_Group == "CPN_5_8", Date >= "2020-01-01")

#CALLABLE
#Callable bonds with coupon intervals of 0-3.5 percent excluding "FED TAXABLE/ST TAX-EXEMPT" Tax province
G1_c_op <- 
  Cal_callable %>%
  filter(CPN_Group == "CPN_0_3.5", Date >= "2020-01-01", 
         MUNI_TAX_PROV != "FED TAXABLE/ST TAX-EXEMPT")

#Callable bonds with coupon intervals of 0-3.5 percent within "FED TAXABLE/ST TAX-EXEMPT" province
G1_c_ft <- Cal_callable %>%
  filter(CPN_Group == "CPN_0_3.5", Date >= "2020-01-01", 
         MUNI_TAX_PROV == "FED TAXABLE/ST TAX-EXEMPT")

#Callable bonds with coupon intervals of 3-5 percent excluding "FED TAXABLE/ST TAX-EXEMPT" province

G2_c_op <- 
  Cal_callable %>% 
  filter(CPN_Group == "CPN_3.5_5", Date >= "2020-01-01", 
         MUNI_TAX_PROV != "FED TAXABLE/ST TAX-EXEMPT"  )


#Callable bonds with coupon intervals of 3.5-5 percent within "FED TAXABLE/ST TAX-EXEMPT" province

G2_c_ft <- 
  Cal_callable %>% 
  filter(CPN_Group == "CPN_3.5_5", Date >= "2020-01-01", 
         MUNI_TAX_PROV == "FED TAXABLE/ST TAX-EXEMPT"  )


#Callable bonds with coupon intervals of 5-8.5 percent excluding "FED TAXABLE/ST TAX-EXEMPT" province

G3_c_all <- Cal_callable %>% 
  filter(CPN_Group == "CPN_5_8.5", Date >= "2020-01-01")

```
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Function for calculating PVs using the fitted yields for approach 2 (EQ.10)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}

bp_calculator_a2 <- function(x, y, m, cuts, bond_type, year_fraction, coupon_rate, 
                          coupon_frequency, face_value) {
  
  bond_price <- 0
  fitted_curve <- lm(y ~ bs(x, degree = m, knots = cuts))
  
  if (bond_type %in% c("FIXED", "FIXED, OID")) {
    C <- face_value * coupon_rate / coupon_frequency
    n <- year_fraction * coupon_frequency
    tau_n <- c(seq(ifelse(n %% 1 == 0.00, 1, n %% 1), n, by = 1) / coupon_frequency)
    
    for (t in tau_n) {
      discounted_cashflow <- 
        C / ((1 + predict(fitted_curve, newdata = data.frame(x = t))/(100*coupon_frequency)) ^ which(tau_n == t))
      bond_price <- bond_price + discounted_cashflow 
    }
    
    final_cashflow <- 
      (face_value) / ((1 + predict(fitted_curve, newdata = data.frame(x = year_fraction))/(100*coupon_frequency)) ^ which(tau_n == year_fraction))
    bond_price <- bond_price + final_cashflow  
  } else if (bond_type == "ZERO COUPON") {
    bond_price <- 
      (face_value) / ((1 + predict(fitted_curve, newdata = data.frame(x = year_fraction))/(100*coupon_frequency)) ^ which(tau_n == year_fraction))
  } else {
    stop("Unsupported bo0nd type")
  }
  
  return(bond_price)
}


```
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Calculating PVs using the green bootstraps curves for the bonds groups (EQ.10)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}
for (i in 1:nrow(G1_nc_all)) {
  x <- G1_nc_all$YF[G1_nc_all$Date == G1_nc_all$Date[i]]
  y <- G1_nc_all$yield[G1_nc_all$Date == G1_nc_all$Date[i]]
  m <- 1
  cuts <- summary(sort(x))[c(2,3,5)]
  bond_type <- G1_nc_all$CPN_TYP[i]
  year_fraction <-  as.numeric(G1_nc_all$YF[i])
  coupon_rate <- as.numeric(G1_nc_all$CPN[i]) / 100
  coupon_frequency <- as.numeric(G1_nc_all$CPN_FREQ[i])
  face_value <- as.numeric(G1_nc_all$PAR_AMT[i])

  gbp <- bp_calculator_a3(x, y, m, cuts, bond_type, year_fraction, coupon_rate,
                          coupon_frequency, face_value)

  G1_nc_all$GPV_3[i] <- gbp
}

```
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Function for calculating Eq. ZCB YTM (EQ.10)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}
zcb_eq_YTM_2 <- function(zcb_ytm, year_fraction,
                           face_value, bond_type, bond_price, 
                          coupon, coupon_frequency) {
  C <- face_value * coupon / coupon_frequency
  n <- year_fraction * coupon_frequency
  tau_n <- c(seq(ifelse(n %% 1 == 0.00, 1, n %% 1), n, by = 1) / coupon_frequency)
  if (bond_type %in% c("FIXED", "FIXED, OID", "ZERO COUPON, OID")) {
    return(((1 + zcb_ytm) ^ which(tau_n == year_fraction)) - ((face_value + C) / bond_price))
  } else {
    stop("Unsupported bond_type")
  }
}

```

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Calculating Equivalent ZCB YTM of green bonds in approach 2 for dataset (EQ.10)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}
for (i in 1:nrow(G3_c_op)) {
  year_fraction <- as.numeric(G3_c_op$YF[i])
  face_value <- as.numeric(G3_c_op$PAR_AMT[i])
  bond_price <- G3_c_op$GPV_2[i]
  coupon <- as.numeric(G3_c_op$CPN[i])/100
  bond_type <- G3_c_op$CPN_TYP[i]
  coupon_frequency <- as.numeric(G3_c_op$CPN_FREQ[i])

  result <- uniroot(zcb_eq_YTM_2, year_fraction = year_fraction, coupon = coupon, bond_type = bond_type,
                    face_value = face_value, coupon_frequency = coupon_frequency, bond_price = bond_price, interval = c(-1, 20))

  G3_c_op$GZCB_YTM_2[i] <- round(result$root * 100, digits = 4)
  
  }

```
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Calculating  Reference Rates
Importing US Treasury Par yield Curve (EQ.11)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}
#Daily Treasury Par Yield Curve Rates

par_data <- read.csv("C:.../daily_par_yield-curve-rates-1990-2023.csv")

names(par_data)[-1] <- c("0.083", "0.167", "0.231", "0.333", "0.500", "1", "2", "3",
"5", "7", "10", "20", "30")
par_data$Date <- dmy(par_data$Date)

par_data_mat <- as.matrix(par_data)
par_data_mat <- par_data_mat[, -1]

par_tby <- as.xts(par_data_mat, order.by = par_data$Date)

par_tby <- na.approx(par_tby, na.rm = FALSE)
```

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Calculating PVs based on the yields Treasury yield curve (EQ.11)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}

for (i in 1:nrow(G2_c_ft)) {
  x <- as.numeric(sort(names(par_tby)))
  y <- as.numeric(par_tby[G2_c_ft$Date[i], sort(names(par_tby))])
  m <- 3
  cuts <- summary(x)[c(2,3,5)]
  bond_type <- G2_c_ft$CPN_TYP[i]
  year_fraction <- as.numeric(G2_c_ft$YF[i])
  coupon_rate <- as.numeric(G2_c_ft$CPN[i]) / 100
  coupon_frequency <- as.numeric(G2_c_ft$CPN_FREQ[i])
  face_value <- as.numeric(G2_c_ft$PAR_AMT[i])

  tr_p_2 <- bp_calculator_a2(x, y, m, cuts, bond_type, year_fraction, coupon_rate,
                       coupon_frequency, face_value)

  G2_c_ft$RPV_2[i] <- tr_p_2
}

```
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Calculating Reference Equivalent ZCB YTM  in approach 2 for Dataset (EQ.11)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```{r}
for (i in 1:nrow(G2_c_ft)) {
  year_fraction <- as.numeric(G2_c_ft$YF[i])
  face_value <- as.numeric(G2_c_ft$PAR_AMT[i])
  bond_price <- G2_c_ft$RPV_2[i]
  coupon_frequency <- as.numeric(G2_c_ft$CPN_FREQ[i])
  coupon <- as.numeric(G2_c_ft$CPN[i])/100
  bond_type <- G2_c_ft$CPN_TYP[i]

  result <- uniroot(zcb_eq_YTM_2, year_fraction = year_fraction, coupon = coupon,
                    face_value = face_value, bond_price = bond_price,
                    coupon_frequency = coupon_frequency, bond_type = bond_type,
                    interval = c(-1, 20))

  G2_c_ft$RZCB_YTM_2[i] <- round(result$root * 100, digits = 4)
  
  }

```

%%%%%%%%%%%%%%%%%%%%
Calculating Spread 2
%%%%%%%%%%%%%%%%%%%%
```{r}

G2_c_ft$S2 <- round(G2_c_ft$GZCB_YTM_2 - G2_c_ft$RZCB_YTM_2, 2)

```

%%%%%%%%%%%%%%%
Save partitions
%%%%%%%%%%%%%%%
```{r}
write_feather(G2_c_ft, "C:/.../G2_c_ft.feather")

write.csv(G2_c_ft,
          file = "C:/.../G2_c_ft.csv",
          row.names = FALSE )

```

%%%%%%%%%%%%%%%%%
Import partitions
%%%%%%%%%%%%%%%%%
```{r}

G1_nc_all <- read_feather("C:/.../G1_nc_all.feather")

G2_nc_op <- read_feather("C:/.../G2_nc_op.feather")

G2_nc_ft <- read_feather("C:/.../G2_nc_ft.feather")

G3_nc_all <- read_feather("C:/.../G3_nc_all.feather")

G1_c_op <- read_feather("C:/.../G1_c_op.feather")

G1_c_ft <- read_feather("C:/.../G1_c_ft.feather")

G2_c_op <- read_feather("C:/.../G2_c_op.feather")

G2_c_ft <- read_feather("C:/.../G2_c_ft.feather")

G3_c_all <- read_feather("C:/.../G3_c_all.feather")


#Combine partitions

California_20_23 <- rbind(G1_nc_all, G2_nc_op, G2_nc_ft, G3_nc_all, G1_c_op, G1_c_ft, 
                 G2_c_op, G2_c_ft, G3_c_all)

#Save the dataset

write_feather(California_20_23, "C:/.../California_20_23.feather")

write.csv(California_20_23,
          file = "C:/.../California_20_23.csv",
          row.names = FALSE )
```
%%%%%%%%%%%%%
Summary Table
%%%%%%%%%%%%%
```{r}
G1 <-  G1_nc_all %>% summarise(
  Group = "1",
  Callability = "Non Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )


G2 <-  G2_nc_ft %>% summarise(
  Group = "2",
  Callability = "Non Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )

G3 <-  G2_nc_op %>% summarise(
  Group = "3",
  Callability = "Non Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )

G4 <- G3_nc_all %>% summarise(
  Group = "4",
  Callability = "Non Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )

G5 <- G1_c_ft %>% summarise(
  Group = "5",
  Callability = "Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )
G6 <- G1_c_op %>% summarise(
  Group = "6",
  Callability = "Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )

G7 <- G2_c_ft %>% summarise(
  Group = "7",
  Callability = "Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )

G8 <- G2_c_op %>% summarise(
  Group = "8",
  Callability = "Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )

G9 <- G3_c_all %>% summarise(
  Group = "9",
  Callability = "Callable",
  Coupon = paste(min(CPN), max(CPN), sep = "-"),
  "Tax Province" = NA,
    Mean = round(mean(yield, na.rm = TRUE), 3),
    Median = round(median(yield, na.rm = TRUE), 3),
    SD = round(sd(yield, na.rm = TRUE), 3)
  )

Groups <- rbind(G1, G2, G3, G4, G5, G6, G7, G8, G9 )
```




